---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# "Law as Data": DataBrew's collaboration with the Santa Fe Institute

## Installation instructions instructions

1. Ensure that the `cmu-bright` font family is installed on your system (font available in the `fonts/cmu-bright` directory).

2. Install the package by running the following within an R session:

```
devtools::install_github('databrew/sfi')
```

## Developer instructions

Clone this repository by running the following from the command line:

```
git clone https://github.com/databrew/sfi
```

Then copy the "Databrew Graphics" folder from the privately shared "Box" drive into the `data-raw` directory of `sfi`.

Finally install the package by setting the working directory to the newly cloned `sfi` repo and running the following:

```
Rscript build_package.R
```


## Usage instructions

### Generate all plots

The below produces `all_plots.pdf` and populates the `figures` directory with individual image files.

```
library(sfi)
generate_all()
```

### Use the SFI "theme"

The package includes `sfi_theme`, a ggplot2-compatible "theme" object which stylizes plots to match SFI's aesthetics. 

```{r}
library(sfi)
library(ggplot2)
df <- data.frame(a = 1:10,
                 b = rnorm(10) + 10,
                 c = sample(letters[1:3], 10, replace = TRUE))
g <- ggplot(data = df,
             aes(x = a,
                 y = b,
                 color = c)) +
  geom_point(size = 5,
             pch = 1) +
  geom_point(size = 5,
             alpha = 0.5) +
  theme(legend.position = 'bottom') +
  scale_color_manual(name = 'Legend',
                     values = make_colors(n = 3,
                                                    bw = TRUE)) +
  labs(x = 'The horizontal x axis',
       y = 'The vertical y axis',
       title = 'Some title',
       subtitle = 'A detailed subtitle')
Rmisc::multiplot(g,
                 g + theme_sfi() +
                   theme(legend.position = 'bottom'),
                 cols = 2)
```