---
output: pdf_document
---

# Plots

\newpage

\begin{center}
\begin{Huge}
Alexander
\end{Huge}
\end{center}

## Alexander



### Figure 4


```{r alexander_figure_4_version_1}
sfi_plot(author = "alexander", figure = "4")[[1]]
```



```{r alexander_figure_4_version_2}
sfi_plot(author = "alexander", figure = "4")[[2]]
```



```{r alexander_figure_4_version_3}
sfi_plot(author = "alexander", figure = "4")[[3]]
```



```{r alexander_figure_4_version_4}
sfi_plot(author = "alexander", figure = "4")[[4]]
```



```{r alexander_figure_4_version_5}
sfi_plot(author = "alexander", figure = "4")[[5]]
```



```{r alexander_figure_4_version_6}
sfi_plot(author = "alexander", figure = "4")[[6]]
```



```{r alexander_figure_4_version_7}
sfi_plot(author = "alexander", figure = "4")[[7]]
```



```{r alexander_figure_4_version_8}
sfi_plot(author = "alexander", figure = "4")[[8]]
```



```{r alexander_figure_4_version_9}
sfi_plot(author = "alexander", figure = "4")[[9]]
```


\newpage

\begin{center}
\begin{Huge}
Feldman
\end{Huge}
\end{center}

## Feldman



### Figure 1


```{r feldman_figure_1_version_1}
sfi_plot(author = "feldman", figure = "1")[[1]]
```



```{r feldman_figure_1_version_2}
sfi_plot(author = "feldman", figure = "1")[[2]]
```



```{r feldman_figure_1_version_3}
sfi_plot(author = "feldman", figure = "1")[[3]]
```



```{r feldman_figure_1_version_4}
sfi_plot(author = "feldman", figure = "1")[[4]]
```




### Figure 2


```{r feldman_figure_2_version_1}
sfi_plot(author = "feldman", figure = "2")[[1]]
```



```{r feldman_figure_2_version_2}
sfi_plot(author = "feldman", figure = "2")[[2]]
```



```{r feldman_figure_2_version_3}
sfi_plot(author = "feldman", figure = "2")[[3]]
```



```{r feldman_figure_2_version_4}
sfi_plot(author = "feldman", figure = "2")[[4]]
```



```{r feldman_figure_2_version_5}
sfi_plot(author = "feldman", figure = "2")[[5]]
```



```{r feldman_figure_2_version_6}
sfi_plot(author = "feldman", figure = "2")[[6]]
```



```{r feldman_figure_2_version_7}
sfi_plot(author = "feldman", figure = "2")[[7]]
```



```{r feldman_figure_2_version_8}
sfi_plot(author = "feldman", figure = "2")[[8]]
```



```{r feldman_figure_2_version_9}
sfi_plot(author = "feldman", figure = "2")[[9]]
```



```{r feldman_figure_2_version_10}
sfi_plot(author = "feldman", figure = "2")[[10]]
```


\newpage

\begin{center}
\begin{Huge}
Frankenreiter
\end{Huge}
\end{center}

## Frankenreiter



### Figure 2


```{r frankenreiter_figure_2_version_1}
sfi_plot(author = "frankenreiter", figure = "2")[[1]]
```



```{r frankenreiter_figure_2_version_2}
sfi_plot(author = "frankenreiter", figure = "2")[[2]]
```



```{r frankenreiter_figure_2_version_3}
sfi_plot(author = "frankenreiter", figure = "2")[[3]]
```



```{r frankenreiter_figure_2_version_4}
sfi_plot(author = "frankenreiter", figure = "2")[[4]]
```



```{r frankenreiter_figure_2_version_5}
sfi_plot(author = "frankenreiter", figure = "2")[[5]]
```



```{r frankenreiter_figure_2_version_6}
sfi_plot(author = "frankenreiter", figure = "2")[[6]]
```



```{r frankenreiter_figure_2_version_7}
sfi_plot(author = "frankenreiter", figure = "2")[[7]]
```



```{r frankenreiter_figure_2_version_8}
sfi_plot(author = "frankenreiter", figure = "2")[[8]]
```



```{r frankenreiter_figure_2_version_9}
sfi_plot(author = "frankenreiter", figure = "2")[[9]]
```



```{r frankenreiter_figure_2_version_10}
sfi_plot(author = "frankenreiter", figure = "2")[[10]]
```




### Figure 3


```{r frankenreiter_figure_3_version_1}
sfi_plot(author = "frankenreiter", figure = "3")[[1]]
```



```{r frankenreiter_figure_3_version_2}
sfi_plot(author = "frankenreiter", figure = "3")[[2]]
```



```{r frankenreiter_figure_3_version_3}
sfi_plot(author = "frankenreiter", figure = "3")[[3]]
```



```{r frankenreiter_figure_3_version_4}
sfi_plot(author = "frankenreiter", figure = "3")[[4]]
```



```{r frankenreiter_figure_3_version_5}
sfi_plot(author = "frankenreiter", figure = "3")[[5]]
```



```{r frankenreiter_figure_3_version_6}
sfi_plot(author = "frankenreiter", figure = "3")[[6]]
```



```{r frankenreiter_figure_3_version_7}
sfi_plot(author = "frankenreiter", figure = "3")[[7]]
```



```{r frankenreiter_figure_3_version_8}
sfi_plot(author = "frankenreiter", figure = "3")[[8]]
```




### Figure 4


```{r frankenreiter_figure_4_version_1}
sfi_plot(author = "frankenreiter", figure = "4")[[1]]
```



```{r frankenreiter_figure_4_version_2}
sfi_plot(author = "frankenreiter", figure = "4")[[2]]
```



```{r frankenreiter_figure_4_version_3}
sfi_plot(author = "frankenreiter", figure = "4")[[3]]
```



```{r frankenreiter_figure_4_version_4}
sfi_plot(author = "frankenreiter", figure = "4")[[4]]
```



```{r frankenreiter_figure_4_version_5}
sfi_plot(author = "frankenreiter", figure = "4")[[5]]
```



```{r frankenreiter_figure_4_version_6}
sfi_plot(author = "frankenreiter", figure = "4")[[6]]
```



```{r frankenreiter_figure_4_version_7}
sfi_plot(author = "frankenreiter", figure = "4")[[7]]
```



```{r frankenreiter_figure_4_version_8}
sfi_plot(author = "frankenreiter", figure = "4")[[8]]
```




### Figure 5


```{r frankenreiter_figure_5_version_1}
sfi_plot(author = "frankenreiter", figure = "5")[[1]]
```



```{r frankenreiter_figure_5_version_2}
sfi_plot(author = "frankenreiter", figure = "5")[[2]]
```



```{r frankenreiter_figure_5_version_3}
sfi_plot(author = "frankenreiter", figure = "5")[[3]]
```



```{r frankenreiter_figure_5_version_4}
sfi_plot(author = "frankenreiter", figure = "5")[[4]]
```



```{r frankenreiter_figure_5_version_5}
sfi_plot(author = "frankenreiter", figure = "5")[[5]]
```



```{r frankenreiter_figure_5_version_6}
sfi_plot(author = "frankenreiter", figure = "5")[[6]]
```




### Figure 5


```{r frankenreiter_figure_5_version_1}
sfi_plot(author = "frankenreiter", figure = "5")[[1]]
```



```{r frankenreiter_figure_5_version_2}
sfi_plot(author = "frankenreiter", figure = "5")[[2]]
```



```{r frankenreiter_figure_5_version_3}
sfi_plot(author = "frankenreiter", figure = "5")[[3]]
```



```{r frankenreiter_figure_5_version_4}
sfi_plot(author = "frankenreiter", figure = "5")[[4]]
```



```{r frankenreiter_figure_5_version_5}
sfi_plot(author = "frankenreiter", figure = "5")[[5]]
```



```{r frankenreiter_figure_5_version_6}
sfi_plot(author = "frankenreiter", figure = "5")[[6]]
```


\newpage

\begin{center}
\begin{Huge}
Livemore
\end{Huge}
\end{center}

## Livemore



### Figure 1


```{r livemore_figure_1_version_1}
sfi_plot(author = "livemore", figure = "1")[[1]]
```



```{r livemore_figure_1_version_2}
sfi_plot(author = "livemore", figure = "1")[[2]]
```



```{r livemore_figure_1_version_3}
sfi_plot(author = "livemore", figure = "1")[[3]]
```



```{r livemore_figure_1_version_4}
sfi_plot(author = "livemore", figure = "1")[[4]]
```


