---
output: pdf_document
---

# Plots

\newpage

\begin{center}
\begin{Huge}
Dumas
\end{Huge}
\end{center}

## Dumas



### Dumas Figure 1

\newpage

(Dumas 1)

```{r, dumas_figure_1_version_1}
sfi_plot(author = "dumas", figure = "1")[[1]]
```


\newpage

(Dumas 1)

```{r, dumas_figure_1_version_2}
sfi_plot(author = "dumas", figure = "1")[[2]]
```


\newpage

(Dumas 1)

```{r, dumas_figure_1_version_3}
sfi_plot(author = "dumas", figure = "1")[[3]]
```


\newpage

(Dumas 1)

```{r, dumas_figure_1_version_4}
sfi_plot(author = "dumas", figure = "1")[[4]]
```


\newpage

(Dumas 1)

```{r, dumas_figure_1_version_5}
sfi_plot(author = "dumas", figure = "1")[[5]]
```


\newpage

\begin{center}
\begin{Huge}
Feldman
\end{Huge}
\end{center}

## Feldman



### Feldman Figure 1

\newpage

(Feldman 1)

```{r, feldman_figure_1_version_1}
sfi_plot(author = "feldman", figure = "1")[[1]]
```


\newpage

(Feldman 1)

```{r, feldman_figure_1_version_2}
sfi_plot(author = "feldman", figure = "1")[[2]]
```


\newpage

(Feldman 1)

```{r, feldman_figure_1_version_3}
sfi_plot(author = "feldman", figure = "1")[[3]]
```


\newpage

(Feldman 1)

```{r, feldman_figure_1_version_4}
sfi_plot(author = "feldman", figure = "1")[[4]]
```


\newpage

(Feldman 1)

```{r, feldman_figure_1_version_5}
sfi_plot(author = "feldman", figure = "1")[[5]]
```


\newpage

(Feldman 1)

```{r, feldman_figure_1_version_6}
sfi_plot(author = "feldman", figure = "1")[[6]]
```


\newpage

(Feldman 1)

```{r, feldman_figure_1_version_7}
sfi_plot(author = "feldman", figure = "1")[[7]]
```


\newpage

(Feldman 1)

```{r, feldman_figure_1_version_8}
sfi_plot(author = "feldman", figure = "1")[[8]]
```




### Feldman Figure 2

\newpage

(Feldman 2)

```{r, feldman_figure_2_version_1}
sfi_plot(author = "feldman", figure = "2")[[1]]
```


\newpage

(Feldman 2)

```{r, feldman_figure_2_version_2}
sfi_plot(author = "feldman", figure = "2")[[2]]
```


\newpage

(Feldman 2)

```{r, feldman_figure_2_version_3}
sfi_plot(author = "feldman", figure = "2")[[3]]
```


\newpage

(Feldman 2)

```{r, feldman_figure_2_version_4}
sfi_plot(author = "feldman", figure = "2")[[4]]
```


\newpage

(Feldman 2)

```{r, feldman_figure_2_version_5}
sfi_plot(author = "feldman", figure = "2")[[5]]
```


\newpage

\begin{center}
\begin{Huge}
Frankenreiter
\end{Huge}
\end{center}

## Frankenreiter



### Frankenreiter Figure 2

\newpage

(Frankenreiter 2)

```{r, frankenreiter_figure_2_version_1}
sfi_plot(author = "frankenreiter", figure = "2")[[1]]
```


\newpage

(Frankenreiter 2)

```{r, frankenreiter_figure_2_version_2}
sfi_plot(author = "frankenreiter", figure = "2")[[2]]
```


\newpage

(Frankenreiter 2)

```{r, frankenreiter_figure_2_version_3}
sfi_plot(author = "frankenreiter", figure = "2")[[3]]
```


\newpage

(Frankenreiter 2)

```{r, frankenreiter_figure_2_version_4}
sfi_plot(author = "frankenreiter", figure = "2")[[4]]
```


\newpage

(Frankenreiter 2)

```{r, frankenreiter_figure_2_version_5}
sfi_plot(author = "frankenreiter", figure = "2")[[5]]
```


\newpage

(Frankenreiter 2)

```{r, frankenreiter_figure_2_version_6}
sfi_plot(author = "frankenreiter", figure = "2")[[6]]
```


\newpage

(Frankenreiter 2)

```{r, frankenreiter_figure_2_version_7}
sfi_plot(author = "frankenreiter", figure = "2")[[7]]
```




### Frankenreiter Figure 3

\newpage

(Frankenreiter 3)

```{r, frankenreiter_figure_3_version_1}
sfi_plot(author = "frankenreiter", figure = "3")[[1]]
```


\newpage

(Frankenreiter 3)

```{r, frankenreiter_figure_3_version_2}
sfi_plot(author = "frankenreiter", figure = "3")[[2]]
```


\newpage

(Frankenreiter 3)

```{r, frankenreiter_figure_3_version_3}
sfi_plot(author = "frankenreiter", figure = "3")[[3]]
```


\newpage

(Frankenreiter 3)

```{r, frankenreiter_figure_3_version_4}
sfi_plot(author = "frankenreiter", figure = "3")[[4]]
```




### Frankenreiter Figure 4

\newpage

(Frankenreiter 4)

```{r, frankenreiter_figure_4_version_1}
sfi_plot(author = "frankenreiter", figure = "4")[[1]]
```


\newpage

(Frankenreiter 4)

```{r, frankenreiter_figure_4_version_2}
sfi_plot(author = "frankenreiter", figure = "4")[[2]]
```


\newpage

(Frankenreiter 4)

```{r, frankenreiter_figure_4_version_3}
sfi_plot(author = "frankenreiter", figure = "4")[[3]]
```


\newpage

(Frankenreiter 4)

```{r, frankenreiter_figure_4_version_4}
sfi_plot(author = "frankenreiter", figure = "4")[[4]]
```




### Frankenreiter Figure 5

\newpage

(Frankenreiter 5)

```{r, frankenreiter_figure_5_version_1}
sfi_plot(author = "frankenreiter", figure = "5")[[1]]
```


\newpage

(Frankenreiter 5)

```{r, frankenreiter_figure_5_version_2}
sfi_plot(author = "frankenreiter", figure = "5")[[2]]
```


\newpage

(Frankenreiter 5)

```{r, frankenreiter_figure_5_version_3}
sfi_plot(author = "frankenreiter", figure = "5")[[3]]
```


\newpage

(Frankenreiter 5)

```{r, frankenreiter_figure_5_version_4}
sfi_plot(author = "frankenreiter", figure = "5")[[4]]
```


\newpage

(Frankenreiter 5)

```{r, frankenreiter_figure_5_version_5}
sfi_plot(author = "frankenreiter", figure = "5")[[5]]
```


\newpage

(Frankenreiter 5)

```{r, frankenreiter_figure_5_version_6}
sfi_plot(author = "frankenreiter", figure = "5")[[6]]
```


\newpage

(Frankenreiter 5)

```{r, frankenreiter_figure_5_version_7}
sfi_plot(author = "frankenreiter", figure = "5")[[7]]
```


\newpage

(Frankenreiter 5)

```{r, frankenreiter_figure_5_version_8}
sfi_plot(author = "frankenreiter", figure = "5")[[8]]
```


\newpage

(Frankenreiter 5)

```{r, frankenreiter_figure_5_version_9}
sfi_plot(author = "frankenreiter", figure = "5")[[9]]
```


\newpage

(Frankenreiter 5)

```{r, frankenreiter_figure_5_version_10}
sfi_plot(author = "frankenreiter", figure = "5")[[10]]
```




### Frankenreiter Figure 6

\newpage

(Frankenreiter 6)

```{r, frankenreiter_figure_6_version_1}
sfi_plot(author = "frankenreiter", figure = "6")[[1]]
```


\newpage

(Frankenreiter 6)

```{r, frankenreiter_figure_6_version_2}
sfi_plot(author = "frankenreiter", figure = "6")[[2]]
```


\newpage

(Frankenreiter 6)

```{r, frankenreiter_figure_6_version_3}
sfi_plot(author = "frankenreiter", figure = "6")[[3]]
```


\newpage

(Frankenreiter 6)

```{r, frankenreiter_figure_6_version_4}
sfi_plot(author = "frankenreiter", figure = "6")[[4]]
```


\newpage

(Frankenreiter 6)

```{r, frankenreiter_figure_6_version_5}
sfi_plot(author = "frankenreiter", figure = "6")[[5]]
```


\newpage

(Frankenreiter 6)

```{r, frankenreiter_figure_6_version_6}
sfi_plot(author = "frankenreiter", figure = "6")[[6]]
```


\newpage

(Frankenreiter 6)

```{r, frankenreiter_figure_6_version_7}
sfi_plot(author = "frankenreiter", figure = "6")[[7]]
```


\newpage

(Frankenreiter 6)

```{r, frankenreiter_figure_6_version_8}
sfi_plot(author = "frankenreiter", figure = "6")[[8]]
```


\newpage

(Frankenreiter 6)

```{r, frankenreiter_figure_6_version_9}
sfi_plot(author = "frankenreiter", figure = "6")[[9]]
```


\newpage

\begin{center}
\begin{Huge}
Laqueur
\end{Huge}
\end{center}

## Laqueur



### Laqueur Figure 1

\newpage

(Laqueur 1)

```{r, laqueur_figure_1_version_1}
sfi_plot(author = "laqueur", figure = "1")[[1]]
```


\newpage

(Laqueur 1)

```{r, laqueur_figure_1_version_2}
sfi_plot(author = "laqueur", figure = "1")[[2]]
```


\newpage

(Laqueur 1)

```{r, laqueur_figure_1_version_3}
sfi_plot(author = "laqueur", figure = "1")[[3]]
```


\newpage

(Laqueur 1)

```{r, laqueur_figure_1_version_4}
sfi_plot(author = "laqueur", figure = "1")[[4]]
```


\newpage

(Laqueur 1)

```{r, laqueur_figure_1_version_5}
sfi_plot(author = "laqueur", figure = "1")[[5]]
```


\newpage

(Laqueur 1)

```{r, laqueur_figure_1_version_6}
sfi_plot(author = "laqueur", figure = "1")[[6]]
```


\newpage

(Laqueur 1)

```{r, laqueur_figure_1_version_7}
sfi_plot(author = "laqueur", figure = "1")[[7]]
```




### Laqueur Figure 2

\newpage

(Laqueur 2)

```{r, laqueur_figure_2_version_1}
sfi_plot(author = "laqueur", figure = "2")[[1]]
```


\newpage

(Laqueur 2)

```{r, laqueur_figure_2_version_2}
sfi_plot(author = "laqueur", figure = "2")[[2]]
```


\newpage

(Laqueur 2)

```{r, laqueur_figure_2_version_3}
sfi_plot(author = "laqueur", figure = "2")[[3]]
```


\newpage

(Laqueur 2)

```{r, laqueur_figure_2_version_4}
sfi_plot(author = "laqueur", figure = "2")[[4]]
```


\newpage

(Laqueur 2)

```{r, laqueur_figure_2_version_5}
sfi_plot(author = "laqueur", figure = "2")[[5]]
```


\newpage

(Laqueur 2)

```{r, laqueur_figure_2_version_6}
sfi_plot(author = "laqueur", figure = "2")[[6]]
```


\newpage

(Laqueur 2)

```{r, laqueur_figure_2_version_7}
sfi_plot(author = "laqueur", figure = "2")[[7]]
```


\newpage

\begin{center}
\begin{Huge}
Livermore
\end{Huge}
\end{center}

## Livermore



### Livermore Figure 1

\newpage

(Livermore 1)

```{r, livermore_figure_1_version_1}
sfi_plot(author = "livermore", figure = "1")[[1]]
```


\newpage

(Livermore 1)

```{r, livermore_figure_1_version_2}
sfi_plot(author = "livermore", figure = "1")[[2]]
```


\newpage

(Livermore 1)

```{r, livermore_figure_1_version_3}
sfi_plot(author = "livermore", figure = "1")[[3]]
```


\newpage

(Livermore 1)

```{r, livermore_figure_1_version_4}
sfi_plot(author = "livermore", figure = "1")[[4]]
```


\newpage

(Livermore 1)

```{r, livermore_figure_1_version_5}
sfi_plot(author = "livermore", figure = "1")[[5]]
```


\newpage

(Livermore 1)

```{r, livermore_figure_1_version_6}
sfi_plot(author = "livermore", figure = "1")[[6]]
```


\newpage

(Livermore 1)

```{r, livermore_figure_1_version_7}
sfi_plot(author = "livermore", figure = "1")[[7]]
```


\newpage

(Livermore 1)

```{r, livermore_figure_1_version_8}
sfi_plot(author = "livermore", figure = "1")[[8]]
```


\newpage

(Livermore 1)

```{r, livermore_figure_1_version_9}
sfi_plot(author = "livermore", figure = "1")[[9]]
```




### Livermore Figure 2

\newpage

(Livermore 2)

```{r, livermore_figure_2_version_1}
sfi_plot(author = "livermore", figure = "2")[[1]]
```


\newpage

(Livermore 2)

```{r, livermore_figure_2_version_2}
sfi_plot(author = "livermore", figure = "2")[[2]]
```




### Livermore Figure 3

\newpage

(Livermore 3)

```{r, livermore_figure_3_version_1}
sfi_plot(author = "livermore", figure = "3")[[1]]
```


\newpage

(Livermore 3)

```{r, livermore_figure_3_version_2}
sfi_plot(author = "livermore", figure = "3")[[2]]
```




### Livermore Figure 4

\newpage

(Livermore 4)

```{r, livermore_figure_4_version_1}
sfi_plot(author = "livermore", figure = "4")[[1]]
```


\newpage

(Livermore 4)

```{r, livermore_figure_4_version_2}
sfi_plot(author = "livermore", figure = "4")[[2]]
```


