---
output: pdf_document
---

# Plots

\newpage

\begin{center}
\begin{Huge}
Alexander
\end{Huge}
\end{center}

## Alexander



### Alexander Figure 4



(Alexander 4)

```{r, alexander_figure_4_version_1}
sfi_plot(author = "alexander", figure = "4")[[1]]
```




(Alexander 4)

```{r, alexander_figure_4_version_2}
sfi_plot(author = "alexander", figure = "4")[[2]]
```




(Alexander 4)

```{r, alexander_figure_4_version_3}
sfi_plot(author = "alexander", figure = "4")[[3]]
```




(Alexander 4)

```{r, alexander_figure_4_version_4}
sfi_plot(author = "alexander", figure = "4")[[4]]
```




(Alexander 4)

```{r, alexander_figure_4_version_5}
sfi_plot(author = "alexander", figure = "4")[[5]]
```




(Alexander 4)

```{r, alexander_figure_4_version_6}
sfi_plot(author = "alexander", figure = "4")[[6]]
```




(Alexander 4)

```{r, alexander_figure_4_version_7}
sfi_plot(author = "alexander", figure = "4")[[7]]
```




(Alexander 4)

```{r, alexander_figure_4_version_8}
sfi_plot(author = "alexander", figure = "4")[[8]]
```




(Alexander 4)

```{r, alexander_figure_4_version_9}
sfi_plot(author = "alexander", figure = "4")[[9]]
```




(Alexander 4)

```{r, alexander_figure_4_version_10}
sfi_plot(author = "alexander", figure = "4")[[10]]
```




(Alexander 4)

```{r, alexander_figure_4_version_11}
sfi_plot(author = "alexander", figure = "4")[[11]]
```




(Alexander 4)

```{r, alexander_figure_4_version_12}
sfi_plot(author = "alexander", figure = "4")[[12]]
```




(Alexander 4)

```{r, alexander_figure_4_version_13}
sfi_plot(author = "alexander", figure = "4")[[13]]
```




(Alexander 4)

```{r, alexander_figure_4_version_14}
sfi_plot(author = "alexander", figure = "4")[[14]]
```




(Alexander 4)

```{r, alexander_figure_4_version_15}
sfi_plot(author = "alexander", figure = "4")[[15]]
```




(Alexander 4)

```{r, alexander_figure_4_version_16}
sfi_plot(author = "alexander", figure = "4")[[16]]
```




(Alexander 4)

```{r, alexander_figure_4_version_17}
sfi_plot(author = "alexander", figure = "4")[[17]]
```




(Alexander 4)

```{r, alexander_figure_4_version_18}
sfi_plot(author = "alexander", figure = "4")[[18]]
```




### Alexander Figure 7



(Alexander 7)

```{r, alexander_figure_7_version_1}
sfi_plot(author = "alexander", figure = "7")[[1]]
```




(Alexander 7)

```{r, alexander_figure_7_version_2}
sfi_plot(author = "alexander", figure = "7")[[2]]
```




(Alexander 7)

```{r, alexander_figure_7_version_3}
sfi_plot(author = "alexander", figure = "7")[[3]]
```




(Alexander 7)

```{r, alexander_figure_7_version_4}
sfi_plot(author = "alexander", figure = "7")[[4]]
```




(Alexander 7)

```{r, alexander_figure_7_version_5}
sfi_plot(author = "alexander", figure = "7")[[5]]
```




(Alexander 7)

```{r, alexander_figure_7_version_6}
sfi_plot(author = "alexander", figure = "7")[[6]]
```


\newpage

\begin{center}
\begin{Huge}
Feldman
\end{Huge}
\end{center}

## Feldman



### Feldman Figure 1



(Feldman 1)

```{r, feldman_figure_1_version_1}
sfi_plot(author = "feldman", figure = "1")[[1]]
```




(Feldman 1)

```{r, feldman_figure_1_version_2}
sfi_plot(author = "feldman", figure = "1")[[2]]
```




(Feldman 1)

```{r, feldman_figure_1_version_3}
sfi_plot(author = "feldman", figure = "1")[[3]]
```




(Feldman 1)

```{r, feldman_figure_1_version_4}
sfi_plot(author = "feldman", figure = "1")[[4]]
```




### Feldman Figure 2



(Feldman 2)

```{r, feldman_figure_2_version_1}
sfi_plot(author = "feldman", figure = "2")[[1]]
```




(Feldman 2)

```{r, feldman_figure_2_version_2}
sfi_plot(author = "feldman", figure = "2")[[2]]
```




(Feldman 2)

```{r, feldman_figure_2_version_3}
sfi_plot(author = "feldman", figure = "2")[[3]]
```




(Feldman 2)

```{r, feldman_figure_2_version_4}
sfi_plot(author = "feldman", figure = "2")[[4]]
```




(Feldman 2)

```{r, feldman_figure_2_version_5}
sfi_plot(author = "feldman", figure = "2")[[5]]
```




(Feldman 2)

```{r, feldman_figure_2_version_6}
sfi_plot(author = "feldman", figure = "2")[[6]]
```




(Feldman 2)

```{r, feldman_figure_2_version_7}
sfi_plot(author = "feldman", figure = "2")[[7]]
```


\newpage

\begin{center}
\begin{Huge}
Frankenreiter
\end{Huge}
\end{center}

## Frankenreiter



### Frankenreiter Figure 2



(Frankenreiter 2)

```{r, frankenreiter_figure_2_version_1}
sfi_plot(author = "frankenreiter", figure = "2")[[1]]
```




(Frankenreiter 2)

```{r, frankenreiter_figure_2_version_2}
sfi_plot(author = "frankenreiter", figure = "2")[[2]]
```




(Frankenreiter 2)

```{r, frankenreiter_figure_2_version_3}
sfi_plot(author = "frankenreiter", figure = "2")[[3]]
```




(Frankenreiter 2)

```{r, frankenreiter_figure_2_version_4}
sfi_plot(author = "frankenreiter", figure = "2")[[4]]
```




(Frankenreiter 2)

```{r, frankenreiter_figure_2_version_5}
sfi_plot(author = "frankenreiter", figure = "2")[[5]]
```




(Frankenreiter 2)

```{r, frankenreiter_figure_2_version_6}
sfi_plot(author = "frankenreiter", figure = "2")[[6]]
```




(Frankenreiter 2)

```{r, frankenreiter_figure_2_version_7}
sfi_plot(author = "frankenreiter", figure = "2")[[7]]
```




(Frankenreiter 2)

```{r, frankenreiter_figure_2_version_8}
sfi_plot(author = "frankenreiter", figure = "2")[[8]]
```




(Frankenreiter 2)

```{r, frankenreiter_figure_2_version_9}
sfi_plot(author = "frankenreiter", figure = "2")[[9]]
```




(Frankenreiter 2)

```{r, frankenreiter_figure_2_version_10}
sfi_plot(author = "frankenreiter", figure = "2")[[10]]
```




(Frankenreiter 2)

```{r, frankenreiter_figure_2_version_11}
sfi_plot(author = "frankenreiter", figure = "2")[[11]]
```




(Frankenreiter 2)

```{r, frankenreiter_figure_2_version_12}
sfi_plot(author = "frankenreiter", figure = "2")[[12]]
```




### Frankenreiter Figure 3



(Frankenreiter 3)

```{r, frankenreiter_figure_3_version_1}
sfi_plot(author = "frankenreiter", figure = "3")[[1]]
```




(Frankenreiter 3)

```{r, frankenreiter_figure_3_version_2}
sfi_plot(author = "frankenreiter", figure = "3")[[2]]
```




(Frankenreiter 3)

```{r, frankenreiter_figure_3_version_3}
sfi_plot(author = "frankenreiter", figure = "3")[[3]]
```




(Frankenreiter 3)

```{r, frankenreiter_figure_3_version_4}
sfi_plot(author = "frankenreiter", figure = "3")[[4]]
```




(Frankenreiter 3)

```{r, frankenreiter_figure_3_version_5}
sfi_plot(author = "frankenreiter", figure = "3")[[5]]
```




(Frankenreiter 3)

```{r, frankenreiter_figure_3_version_6}
sfi_plot(author = "frankenreiter", figure = "3")[[6]]
```




(Frankenreiter 3)

```{r, frankenreiter_figure_3_version_7}
sfi_plot(author = "frankenreiter", figure = "3")[[7]]
```




(Frankenreiter 3)

```{r, frankenreiter_figure_3_version_8}
sfi_plot(author = "frankenreiter", figure = "3")[[8]]
```




### Frankenreiter Figure 4



(Frankenreiter 4)

```{r, frankenreiter_figure_4_version_1}
sfi_plot(author = "frankenreiter", figure = "4")[[1]]
```




(Frankenreiter 4)

```{r, frankenreiter_figure_4_version_2}
sfi_plot(author = "frankenreiter", figure = "4")[[2]]
```




(Frankenreiter 4)

```{r, frankenreiter_figure_4_version_3}
sfi_plot(author = "frankenreiter", figure = "4")[[3]]
```




(Frankenreiter 4)

```{r, frankenreiter_figure_4_version_4}
sfi_plot(author = "frankenreiter", figure = "4")[[4]]
```




(Frankenreiter 4)

```{r, frankenreiter_figure_4_version_5}
sfi_plot(author = "frankenreiter", figure = "4")[[5]]
```




(Frankenreiter 4)

```{r, frankenreiter_figure_4_version_6}
sfi_plot(author = "frankenreiter", figure = "4")[[6]]
```




(Frankenreiter 4)

```{r, frankenreiter_figure_4_version_7}
sfi_plot(author = "frankenreiter", figure = "4")[[7]]
```




(Frankenreiter 4)

```{r, frankenreiter_figure_4_version_8}
sfi_plot(author = "frankenreiter", figure = "4")[[8]]
```




### Frankenreiter Figure 5



(Frankenreiter 5)

```{r, frankenreiter_figure_5_version_1}
sfi_plot(author = "frankenreiter", figure = "5")[[1]]
```




(Frankenreiter 5)

```{r, frankenreiter_figure_5_version_2}
sfi_plot(author = "frankenreiter", figure = "5")[[2]]
```




(Frankenreiter 5)

```{r, frankenreiter_figure_5_version_3}
sfi_plot(author = "frankenreiter", figure = "5")[[3]]
```




(Frankenreiter 5)

```{r, frankenreiter_figure_5_version_4}
sfi_plot(author = "frankenreiter", figure = "5")[[4]]
```




(Frankenreiter 5)

```{r, frankenreiter_figure_5_version_5}
sfi_plot(author = "frankenreiter", figure = "5")[[5]]
```




(Frankenreiter 5)

```{r, frankenreiter_figure_5_version_6}
sfi_plot(author = "frankenreiter", figure = "5")[[6]]
```




### Frankenreiter Figure 6



(Frankenreiter 6)

```{r, frankenreiter_figure_6_version_1}
sfi_plot(author = "frankenreiter", figure = "6")[[1]]
```




(Frankenreiter 6)

```{r, frankenreiter_figure_6_version_2}
sfi_plot(author = "frankenreiter", figure = "6")[[2]]
```




(Frankenreiter 6)

```{r, frankenreiter_figure_6_version_3}
sfi_plot(author = "frankenreiter", figure = "6")[[3]]
```




(Frankenreiter 6)

```{r, frankenreiter_figure_6_version_4}
sfi_plot(author = "frankenreiter", figure = "6")[[4]]
```




(Frankenreiter 6)

```{r, frankenreiter_figure_6_version_5}
sfi_plot(author = "frankenreiter", figure = "6")[[5]]
```




(Frankenreiter 6)

```{r, frankenreiter_figure_6_version_6}
sfi_plot(author = "frankenreiter", figure = "6")[[6]]
```




(Frankenreiter 6)

```{r, frankenreiter_figure_6_version_7}
sfi_plot(author = "frankenreiter", figure = "6")[[7]]
```




(Frankenreiter 6)

```{r, frankenreiter_figure_6_version_8}
sfi_plot(author = "frankenreiter", figure = "6")[[8]]
```


