
\begin{longtable}{ll>{\raggedright\arraybackslash}p{30em}lll}
\toprule
Case number & Docket text & Paired order text & Filled by & Adoption & Case ended\\
\midrule
1:10-cv-00007-JEC & FINAL REPORT AND RECOMMENDATION recommending GRANTING 22 MOTION for Summary Judgment as to all of Plaintiff's claims. Signed by Magistrate Judge Gerrilyn G. Brill on 06/14/11. (Attachments: \# 1 Order for Service)(fap) (Entered: 06/15/2011) * & ORDER regarding Magistrate Judge's Final Report and Recommendation. IT IS HEREBY ORDERED that the Court ADOPTS the Magistrate Judge's Final Report and Recommendation 28 GRANTING defendants' Motion for Summary Judgment as to all of plaintiff's claim 22 . The Clerk is directed to close this action. Signed by Judge Julie E. Carnes on 7/5/11. (cem) (Entered: 07/06/2011) * * * * & defendant & adopt & Yes\\
1:10-cv-00383-ODE & REPORT AND RECOMMENDATION that Defendant's 42 MOTION for Summary Judgment be GRANTED IN PART AND DENIED IN PART. Specifically, the undersigned RECOMMENDS that the motion for summary judgment be DENIED with respect to Plaintiffs' Title VII claims, DENIED with respect to Plaintiffs’ S. 1981 claims, and GRANTED with respect to Plaintiff Lewis, Power, and Johnson's claims under the Equal Protection Clause. Signed by Magistrate Judge Alan J. Baverman on 1/31/2012. (rej) (Entered: 02/01/2012) * & ORDER that City of Kennesaw's Objections are 56 SUSTAINED and the 55 Report and Recommendation is ADOPTED IN PART AND REJECTED IN PART. The City of Kennesaw's 42 Motion for Summary Judgment is GRANTED in accordance with Federal Rule of Civil Procedure 56(a) because Plaintiffs have failed to establish a prima facie case of discrimination. Signed by Judge Orinda D. Evans on 3/30/2012. (anc) (Entered: 03/30/2012) * * * * & defendant & partial & No\\
\bottomrule
\end{longtable}